### 2020-07-25 draft.Rmd
Edit some typos and add more comments to the R code

```{r}
skewa <- six_months %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

@@

```{r}
skewa <- six_months %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha = 0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal() +
  guides(color = FALSE)

@@

```{r}
# 12 months 
treated <-  treated %>%
  mutate(change =
           case_when(
             balchange > 0 ~ "Increase",
             balchange == 0 ~ "No Change",
             balchange < 0 ~ "Decrease"
           )
  ) %>%
  mutate(change = factor(change, levels = c("Decrease", "No Change", "Increase")))

@@

```{r}
count(treated, group, change) %>%
  knitr::kable(caption = "Change in Balance After Twelve Months by Treatment Group")
```

@@

```{r}

count(treated, frac_change_20) %>%
  knitr::kable(caption = "20+% Change in Balance After Twelve Months")

count(treated, group, frac_change_20) %>%
  knitr::kable(caption = "20+% Change in Balance After Twelve Months")
```

@@

```{r results = "asis"}
six_months <- filter(seed011204, !is.na(treatment))

@@

M-estimation leads to results that look very different than [@Ashraf2006]. Column (1) shows the change in balance after six months including all observations. The coefficients estimate the additional savings of the corresponding treatment over the control group. Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group. Column (3) is similar to column (1), only it uses the twelve month change in balance. Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.

In all four cases the estimated intercept is negative and the coefficients, while positive, are smaller in magnitude than the OLS model. That means the conditional means for the commitment savings group, the marketing control group, and the control group are all negative. That said, the estimated intent-to-treat effect is statistically significantly different in three of the four specifications. However, the treatment effects are very small.

```{r results = "asis"}
# column 1
m_model1 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)

@@

Robust and rank-based regression leads to results that look very different than [@Ashraf2006]. Column (1) shows the change in balance after six months including all observations. The coefficients estimate the additional savings of the corresponding treatment over the control group. Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group. Column (3) is similar to column (1), only it uses the twelve month change in balance. Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.

```{r results = "asis"}
# column 1
rank_model1 <- rfit(balchange ~ treatment + marketing, data = six_months)

@@

The weight of the positive outliers leads to a positive estimated intercept and larger estimated coefficients for the treatments in the OLS model. The other two models, which are more robust to outliers, have negative estimated intercepts and estimated coefficients for the treatments that are much closer to zero.

@@

```{r}
lm3 <- lm(balchange ~ treatment + marketing, data = treated) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

@@

```{r}
lm4 <- lm(balchange ~ treatment, 
   data = filter(treated, group %in% c("M", "T"))) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

>>>>

```{r}
#
# Create a plot to show the skew of balchange
#
skewa <- six_months %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

@@

```{r}
#
# Create a plot to show the skew of balchange by group
#
skewa <- six_months %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha = 0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal() +
  guides(color = FALSE)

@@

```{r}
#
# Count the types of change in balchange
# 
treated <-  treated %>%
  mutate(change =
           case_when(
             balchange > 0 ~ "Increase",
             balchange == 0 ~ "No Change",
             balchange < 0 ~ "Decrease"
           )
  ) %>%
  mutate(change = factor(change, levels = c("Decrease", "No Change", "Increase")))

@@

```{r}
count(treated, group, change) %>%
  knitr::kable(caption = "Change in Balance After Twelve Months by Treatment Group")

@@

```{r}
count(treated, frac_change_20) %>%
  knitr::kable(caption = "20+% Change in Balance After Twelve Months")

count(treated, group, frac_change_20) %>%
  knitr::kable(caption = "20+% Change in Balance After Twelve Months")

@@

```{r results = "asis"}
#
# OLS model
#
six_months <- filter(seed011204, !is.na(treatment))

@@

We estimate identical specifications to [@Ashraf2006] using M-estimation. Column (1) shows the change in balance after six months including all observations. The coefficients estimate the additional savings of the corresponding treatment over the control group. Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group. Column (3) is similar to column (1), only it uses the twelve month change in balance. Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.

```{r results = "asis"}
#
# M-Estimation model
#

# column 1
m_model1 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)

@@

We estimate identical specifications to [@Ashraf2006] using robust and rank-based regressions. Column (1) shows the change in balance after six months including all observations. The coefficients estimate the additional savings of the corresponding treatment over the control group. Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group. Column (3) is similar to column (1), only it uses the twelve month change in balance. Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.

```{r results = "asis"}
#
# Robust and rank-based regression
#

# column 1
rank_model1 <- rfit(balchange ~ treatment + marketing, data = six_months)

@@

The weight of the positive outliers leads to a positive estimated intercept and larger estimated coefficients for the treatments in the OLS model. The other two models, which are more robust to outliers, have negative estimated intercepts and estimated coefficients for the treatments that are much closer to zero. For M-estimation and robust ranked based regression, the estimated intercepts are negative and the coefficients, while positive, are smaller in magnitude than the OLS model. That means the conditional means for the commitment savings group, the marketing control group, and the control group are all negative.

@@

```{r}
#
# Visualize column (3)
#

lm3 <- lm(balchange ~ treatment + marketing, data = treated) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

@@

```{r}
#
# Visualize column (4)
#

lm4 <- lm(balchange ~ treatment, 
   data = filter(treated, group %in% c("M", "T"))) %>%
  coeftest(vcov = vcovHC(., type="HC1"))
